{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-06 wacv_for_review.tex
Added more comments.

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background bigger than that of the first filter, $R_{t}^{S}$, \textit{target}+\textit{large background}. 
We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target {\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.} 
  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
  translation filter needs background whereas the scale filter does not.}
Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.

@@

@@

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

@@

@@

>>>>

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}.

We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target

{\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.}

{\it YoungWoo : In this paragraph, we mention two of the translation
  filters and then we say translation filter needs background whereas
  the scale filter does not.}

{\it Burak: The paragraph I'm referring to begins ``We set up...'' The
  paragraph before this explain what each of the KCFs is for, but
  didn't say why at the next paragraph ``We set up...''}

Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.

@@

{\it Burak: I don't think that's a good way of arranging this. You
  talked about EnKCF, then KCF should come out before any variants of
  KCF w/ conventional feature and w/ deep features. Otherwise, what is
  the point of having KCF section after you explained all the usage of
  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
  deep features. Given this order, two paragraphs before and after
  this didn't connect!}

@@

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI.

{\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?}

{\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$
  to have similar fps (30fps) to avoid missing frames on an embedded
  system. We can think of each one as an individual tracker and we do
  not want one operating at 10fps while others running at 30 fps.}

{\it Burak: What you told me is purely empirical which is fine. But
  you'll have to tell the readers why we wanted to keep the run-time
  complexity of those filters same!}

By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

@@

{\it Burak: We can put these together if their performances from the
  same data -- don't need to use the same features to be on the same
  graph! We said EnKCF w/ deep features improved the performance, then
  what's the point to separate them into two graphs?}

@@

{\it Burak: Earlier we told the readers why we wanted to have two
  translation filters: one for smaller region, $R_{t}^{S}$, and
  another for larger region, $R_{t}^{L}$. The reason why we have two
  translation filter, instead of one because we wanted to minimize any
  drifts, yes? Read the line from 354 to 374. Then if we say again
  here we have a particle filter for smoothing transition among KCFs,
  they might think those two translation filters do not do their jobs
  well?}
